### 2017-10-15 ch362/latex/report3.tex

Mass spectrometry (MS) and NMR are invaluable techniques for structure elucidation of unknown organic molecules. When a molecule is sufficiently simple, knowledge of its molecular weight, carbon number, and rough identity of carbons and hydrogens can be enough to uniquely determine identity. For more complex molecules, or those with many isomers, further information from 2D experiments like $^{13}$C-$^{1}$H HSQC or $^{13}$C-$^{1}$H HMBC may be necessary.\\

This article follows the designation of a disubstituted benzene unknown using the above techniques. MS is used to determine weight, $^{13}$C NMR is used to come up with a candidate structure, $^{1}$H NMR is used to verify this candidate and guess its substitution, and $^{13}$C-$^{1}$H HSQC is used to verify the substitution.\\

@@

\section{$^{13}$C NMR}
The $^{13}$C NMR spectra shown in Figure \ref{fig:CNMR} has 9 peaks. As shown in Table \ref{table:MS}, one peak is due to a DMSO solvent, six to aromatic carbons, one to a methyl carbon and one to a carboxylic carbon. These results agree with the 8-carbon estimate from peak ratios in MS.\\

\begin{figure}[h]
\centering
  \includegraphics[height=5cm]{figures/CNMR.png}
  \caption{$^{13}$C NMR of \textit{Sample 8}.}
  \label{fig:CNMR}
\end{figure}

@@

\section{$^{1}$H NMR}

\begin{figure}[h]
\centering
  \includegraphics[height=5cm]{figures/HNMR.png}
  \caption{$^{1}$H NMR of \textit{Sample 8}.}
  \label{fig:HNMR}
\end{figure}

\begin{table}[h]
\small
  \caption{$^{13}$C NMR identified peaks for spectra shown in Figure \ref{fig:HNMR}.}
  \label{table:HNMR}
  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}llll}
    \hline
    Peak(s) shift(s) ppm & Integration & Splitting & Designation \\
    \hline
    2.3 & 3.1 & Singlet & Ar-CH$_3$ hydrogens\\
    2.4 & 0.4 & Pentet & DMSO\\
    7.35 & 1.1 & Singlet & Aromatic H\\
    7.4 & 1.0 &  Meta Doublet & Aromatic H\\
    7.72 & 1.1 & Meta Doublet & Aromatic H\\
    7.75 & 1.1 & Singlet & Aromatic H\\
    12.8 & 1.0 & Singlet & Carboxylic H\\
    \hline
  \end{tabular*}
\end{table}

\section{Equations}

@@

\footnotesize{
\bibliography{rsc} %your .bib file
\bibliographystyle{rsc} %the RSC's .bst file
}

\end{document}

>>>>

Mass spectrometry (MS) and NMR are invaluable techniques for structure elucidation of unknown organic molecules. When a molecule is sufficiently simple, knowledge of its molecular weight, carbon number, and the shifts of its carbons and hydrogens can be enough to uniquely determine identity. For more complex molecules, or those with many isomers, further information from 2D experiments like $^{13}$C-$^{1}$H HSQC or $^{13}$C-$^{1}$H HMBC may be necessary.\\

This article follows the designation of a disubstituted benzene unknown using the above techniques. MS is used to determine weight, $^{13}$C NMR is used to come up with a candidate structure, $^{1}$H NMR is used to verify this candidate and guess its substitution, and $^{13}$C-$^{1}$H HSQC/HMBC are used to verify the substitution.\\

@@

\section{$^{13}$C NMR}
The $^{13}$C NMR spectra shown in Figure \ref{fig:CNMR} has 9 peaks. Comparison with online shift reports [2] indicate one peak is due to a DMSO solvent, six to aromatic carbons, one to a methyl carbon and one to a carboxylic carbon, as shown in Table \ref{table:MS}. These results agree with the 8-carbon estimate from peak ratios in MS.\\

\begin{figure}[h]
\centering
  \includegraphics[height=4.5cm]{figures/CNMR.png}
  \caption{$^{13}$C NMR of \textit{Sample 8}.}
  \label{fig:CNMR}
\end{figure}

@@

\section{$^{1}$H NMR}
$^{1}$H NMR is then used to get more information on substitutuent placement. A spectra is shown in Figure \ref{fig:HNMR} with annotated peaks shown in Table \ref{table:HNMR} indicating the presence of a carboxylic hydrogen at 12.8ppm and methyl hydrogens at 2.3ppm [2], verifying the methyl benzoic acid hypothesis. The splitting pattern of the aromatic hydrogens shown in Figure \ref{fig:HNMR-closeup} is used to determine configuration. Because four unique aromatic peaks are visible, the \textit{para} configuration is impossible. The presence of a singlet aromatic peak rules out \textit{ortho} and suggests \textit{meta} as the substitution pattern.\\

The \textit{meta} designation is further evidenced by the presence of very small, 1-Hz meta coupling of the two doublet hydrogens. This coupling is expected between the singlet hydrogen and the two hydrogens adjacent to only one substitute group.\\

\begin{figure}[h]
\centering
  \includegraphics[height=4cm]{figures/HNMR.png}
  \caption{$^{1}$H NMR of \textit{Sample 8}.}
  \label{fig:HNMR}
\end{figure}

\begin{figure}[h]
\centering
  \includegraphics[height=1.2cm]{figures/HNMR-splitting.png}
  \caption{Close-up of aromatic peaks in $^{1}$H NMR spectra of \textit{Sample 8}.}
  \label{fig:HNMR-closeup}
\end{figure}

\begin{table}[h]
\small
  \caption{$^{1}$H NMR identified peaks for spectra shown in Figure \ref{fig:HNMR}.}
  \label{table:HNMR}
  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}llll}
    \hline
    Shift(s) ppm & Integration & Splitting & Designation \\
    \hline
    2.3 & 3.1 & Singlet & Ar-CH$_3$ hydrogens\\
    2.4 & 0.4 & Pentet & DMSO\\
    7.35 & 1.1 & Singlet & Aromatic H\\
    7.4 & 1.0 &  Meta Doublet & Aromatic H\\
    7.72 & 1.1 & Meta Doublet & Aromatic H\\
    7.75 & 1.1 & Singlet & Aromatic H\\
    12.8 & 1.0 & Singlet & Carboxylic H\\
    \hline
  \end{tabular*}
\end{table}

\section{COSY}
The COSY spectrum of \textit{Sample 8} is not terribly useful. It verifies that aromatic hydrogens couple to one another, but HMBC provides much more information.

\begin{figure}[h]
\centering
  \includegraphics[height=7cm]{figures/cosy.png}
  \caption{COSY spectrum of \textit{Sample 8}.}
  \label{fig:COSY}
\end{figure}

\section{HSQC}
HSQC is similarly barren of information. The spectrum shown in Figure \ref{fig:HSQC} shows expected coupling between the solvent carbon and hydrogen, between the methyl carbon and methyl protons, and between aromatic carbons and aromatic hydrogens, as expected. More conclusively demonstrated is the presence of four different aromatic hydrogens, further verifying the molecule is not in the para configuration.\\

\begin{figure}[h]
\centering
  \includegraphics[height=7cm]{figures/HSQC.png}
  \caption{HSQC spectrum of \textit{Sample 8}. A blowup of the aromatic region is shown in the middle of the spectrum.}
  \label{fig:HSQC}
\end{figure}

\section{HMBC}
Now that the structure has been determined, individual carbons and hydrogens can be aligned with their respective peaks. Figure \ref{fig:3MBA} shows the candidate molecule along with labels for carbons and hydrogens.\\

\begin{figure}[h]
\centering
  \includegraphics[height=5cm]{figures/molecule.png}
  \caption{3-methylbenzoic acid.}
  \label{fig:3MBA}
\end{figure}

Hydrogen peak placement is easy. The singlet hydrogen must correspond to the carbon between the two substituents. The triplet hydrogen must correspond to the hydrogen diametrically opposed to this carbon. This leaves the two doublet carbons. They can be distinguished by looking at the HMBC spectra shown in Figure \ref{fig:hydromethyl}. Hydrogen H2, indicated in Table \ref{table:H-peaks}, or the upfield doublet, correlates well with the methyl carbon. Carbon H4 is identified by exclusion.\\

An HMBC-HSQC overlay in the aromatic region provides much information about aromatic carbon peaks. Such a spectrum is shown in Figure \ref{fig:overlay}. Carbons C2, C4, C5 and C6 can be easily determined as the carbons which HSQC-correlate with the respective hydrogens H1, H2, H3 and H4, as shown in Table \ref{table:C-peaks}. This leaves the two substituent aromatic carbons to label. Figure \ref{fig:methylaromatic} indicates three carbons pair strongly with the methyl hydrogen: carbons C2 and C4, already labeled, and one of the two substituent carbons shifted furthest downfield of the aromatic carbons. This is likely carbon C1, since 4-bond coupling is much stronger in HMBC spectra than 2-bond coupling. Thus C1 must be the carboxylic substituent aromatic carbon, and thus C3 must be the methyl aromatic carbon. These findings are catalogued in the tables below.\\

\begin{figure}[h]
\centering
  \includegraphics[height=5cm]{figures/HMBC-hydromethyl.png}
  \caption{A closeup of methyl carbon-aromatic hydrogen HMBC coupling.}
  \label{fig:hydromethyl}
\end{figure}

\begin{figure}[h]
\centering
  \includegraphics[height=5cm]{figures/hmbc-methylaromatic.png}
  \caption{A closeup, edited image hilighting HMBC coupling between aromatic carbons and methyl hydrogens.}
  \label{fig:methylaromatic}
\end{figure}

\begin{figure*}
\centering
  \includegraphics[height=10cm]{figures/Overlay.png}
  \caption{HSQC-HMBC overlay in the C, H aromatic region.}
  \label{fig:overlay}
\end{figure*}

\begin{table}[h]
\small
  \caption{Aromatic hydrogen peak identification. In correspondence with the labels shown in Figure \ref{fig:3MBA}.}
  \label{table:H-peaks}
  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}llll}
    \hline
    Shift(s) ppm & Designation \\
    \hline
    7.35 & H3 triplet hydrogen\\
    7.4  & H2 doublet hydrogen\\
    7.72 & H4 doublet hydrogen\\
    7.75 & H1 singlet hydrogen\\
    \hline
  \end{tabular*}
\end{table}

\begin{table}[h]
\small
  \caption{Aromatic carbon peak identification. In correspondence with the labels shown in Figure \ref{fig:3MBA}.}
  \label{table:C-peaks}
  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}llll}
    \hline
    Shift(s) ppm & Designation \\
    \hline
    127 & Carbon 6\\
    129 & Carbon 5\\
    130 & Carbon 2\\
    131 & Carbon 3\\
    134 & Carbon 4\\
    139 & Carbon 1\\
    \hline
  \end{tabular*}
\end{table}

@@

\begin{@twocolumnfalse}
\section{References}
[1] Experimental Chemistry I: CH 362, OSU Department of Chemistry 2017\\

[2] OSU of Chemistry. 1H NMR Chemical Shifts. http://www.science.oregonstate.edu/~gablek/CH335/Chapter10/ChemicalShift.htm. (Accessed March 22, 2017)\\
\end{@twocolumnfalse}
\end{document}
